Enhancement of SDR in Thessaloniki

### 2024-06-27 GHI_enh_04_investigate.tex
Commit 2024-06-27 16:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-06-12}

@@

\caption{ - empty caption - }\label{fig:groups-4}
\end{figure}

@@

\caption{ - empty caption - }\label{fig:groups-10}
\end{figure}

@@

\begin{verbatim}
2024-06-12 08:50:47.4 athan@tyler GHI_enh_04_investigate.R 1.594768 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-06-27}

@@

\caption{ - empty caption - }\label{fig:groups-4}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-10}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-11}

\caption{ - empty caption - }\label{fig:groups-11}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-12}

\caption{ - empty caption - }\label{fig:groups-12}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-13}

\caption{ - empty caption - }\label{fig:groups-13}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-14}

\caption{ - empty caption - }\label{fig:groups-14}
\end{figure}

@@

\begin{verbatim}
2024-06-27 02:44:09.1 athan@tyler GHI_enh_04_investigate.R 2.523809 mins
\end{verbatim}
